\textbf{Technical Report:} \\ Real-Time Certified Probabilistic Pedestrian Forecasting

### 2017-06-09 revision/paper/response.tex

\author{Henry O. Jacobs, Owen K. Hughes, \\ Matt Johnson-Roberson, and Ram Vasudevan }

\begin{document}
\maketitle

%\todo{More formal version of: We would like to thank the reviewers for their comments. The feedback is very helpful, and we have attempted to address everything.}

We would like to begin by thanking the reviewers and the editor for their careful reading and review of our paper.
The comments provided were incredibly helpful and insightful, and have strengthened the paper considerably.
Based on the recommendations of the reviewers and the editor, we have made several modifications to the paper including performing additional analyses with an lstm-based approach and using the Modified Hausdorff Distance metric. 
These additions pushed the paper beyond the eight page limit. 
As a result we removed all proofs from the resubmitted manuscript, but have included them instead in a supplementary technical report with our resubmission.
This technical report will be posted to our websites if the paper is accepted. 
%The changes made are presented below as a highlighted manuscript that indicates additions in green and removals in red.
The changes made are summarized in detail in the letter below. Following the letter is an annotated version of the paper showing the changes made, followed by the technical report. \textbf{This letter is largely self contained, so references here are to the bibliography in this document}.
% See the response to reviewers for a detailed breakdown of the changes made.

@@

	In addition, we evaluated the Modified Hausdorff Distance (MHD) from the ground truth trajectory to a sample from the predictions at each time to provide a geometric measure of how accurate the predictions are. 
	Figure \ref{MHD} shows MHD plotted against time.
	Though popular in evaluating the geometric proximity of the ground truth trajectory and a predicted set, it is not the most appropriate way to evaluate the utility of an algorithm in the autonomous vehicle context. 
	Specifically consider the instance of a generated set of predictions which does not contain the ground-truth observed trajectory but is close to the ground-truth trajectory geometrically. 
	If this generated set of predictions was used in the autonomous vehicle context, it would not preclude certain portions of the space where the person was occupying. 
	Notice that the true positive rate would be zero meaning that the generated set of predictions was not useful.
	Whereas the MHD would describe this generated set of predictions as informative.
}

\begin{figure}
	\centering
	\includegraphics[width=0.6\textwidth]{figures/the_results.eps}
	\caption{A comparison of the AUC of the various algorithms. Note that the initial dip in the performance of \cite{Kitani2012} is due to their confidence in their initial estimate. We sampled the S-LSTM \cite{Alahi2016} model $100$ times to organically extract a less concentrated probability distribution from their algorithm, but their confidence combined with the over-reliance on social forces at moderate-to-large timescales lowered their performance.}
	\reversemarginpar\marginnote{\#4.7}
	\label{AUC}
\end{figure}

\end{item}
\begin{figure}
	\centering
	\includegraphics[width=0.6\textwidth]{figures/mhd_results.eps}
	\caption{A comparison of the MHD from the ground truth of the pedestrian to a 1000 point samples from each distribution. The method from \cite{Alahi2016} does well at short time scales since it places a highly confident distribution at the given initial position of the pedestrian, but the method developed in this paper outperforms all others at intermediate times. At longer timescales the MHD to the trajectory of most algorithms converges. \cite{Kitani2012}, which requires the end point of each trajectory, outperforms all other algorithms which assume that the end point of the trajectory is unknown.}
   \reversemarginpar\marginnote{\#4.8}
	\label{MHD}
\end{figure}

@@

Thank you for this relevant question.
As stated in \cite{Morris2009}, the choice of clustering technique is not nearly as important as the distance metric. 
Our success with distance functions that took a whole trajectory was limited on the data we tested and we found more success using a custom distance metric that only considered the start and end points of a trajectory as we describe in Comment \ref{distmetric} to Reviewer 1. 
We have several hypotheses as to why this is true.  
For one, the spatial scale of the data we test against showcases important features (e.g. curb cuts and storefronts), which lead to clustered start points and end points. 
Similarly, we tested against high quality data in which trajectories with irreconcilable occlusions were rare and thus could be omitted.

\begin{item}
\textbf{Do you cluster different scenes provided in campus dataset \cite{Alahi2016} (i.e
Valley, Fangron) separately or all together? When motion models are
learnt, are they learnt in scene specific manner or altogether?}
\end{item}

Thank you for noticing that this is unclear. 
Our algorithm trains on each scene independently, so clustering, vector field learning, and learning the potential functions are all done for each scene separately. 
To make this more clear, we added the following text to the paper:

\reversemarginpar\marginnote{\#4.2}
\response{We performed a 2-fold cross validation by using 20\% of the data for testing and the remainder for training within each scene. 
We learned separate collections of vector fields and model parameters for each fold on all of the four scenes on which we tested.}

@@

\begin{item} \label{distmetric}
\textbf{The motivation behind choosing the affinity propagation clustering algorithm is not clearly stated. 
What is the distance measure used (i.e Euclidian) ? 
Not specifying such information makes reproduction of this work not feasible. }

This was an oversight on our part, thank you for noticing it. 
The distance used is a custom distance function. 
Let one trajectory $A$ start at $(x_{A,\mathrm{start}}, y_{A,\mathrm{start}})$ and end at  $(x_{A,\mathrm{end}}, y_{A,\mathrm{end}})$, and another trajectory $B$ start at $(x_{B,\mathrm{start}}, y_{B,\mathrm{start}})$ and end at $(x_{B,\mathrm{end}}, y_{B,\mathrm{end}})$ . 
We define the points $\mathbf{a}_1 = (x_{A, \mathrm{start}}, y_{A, \mathrm{start}}, x_{A, \mathrm{end}}, y_{A, \mathrm{end}})$, $\mathbf{a}_2 = (x_{A, \mathrm{end}}, y_{A, \mathrm{end}}, x_{A, \mathrm{start}}, y_{A, \mathrm{start}})$, and $\mathbf{b} = (x_{B, \mathrm{start}}, y_{B, \mathrm{start}}, x_{B, \mathrm{end}}, y_{B, \mathrm{end}})$. 
We then define our distance measure as $d(A, B) :=  \min \left\{ d_e(\mathbf{a}_1, \mathbf{b}), d_e(\mathbf{a}_2, \mathbf{b}) \right\}$, for the euclidean distance $d_e$ in $\mathbb{R}^4$.  This is designed such that transposing endpoints of a trajectory doesn't matter, and so a trajectory that starts at point A and ends at point B is close to a trajectory that starts at point B and ends at point A.  
We have included the following clarification:

\reversemarginpar\marginnote{\#4.1}
\response{To do this, we use a clustering algorithm on the trajectories using Affinity Propagation \cite{FreyDueck2007} and a custom distance measure defined on the endpoints of trajectories. 
	Let one trajectory $A$ start at $(x_{A,\mathrm{start}}, y_{A,\mathrm{start}})$ and end at  $(x_{A,\mathrm{end}}, y_{A,\mathrm{end}})$, and another trajectory $B$ start at $(x_{B,\mathrm{start}}, y_{B,\mathrm{start}})$ and end at $(x_{B,\mathrm{end}}, y_{B,\mathrm{end}})$ . 
	We define the points $\mathbf{a}_1 = (x_{A, \mathrm{start}}, y_{A, \mathrm{start}}, x_{A, \mathrm{end}}, y_{A, \mathrm{end}})$, $\mathbf{a}_2 = (x_{A, \mathrm{end}}, y_{A, \mathrm{end}}, x_{A, \mathrm{start}}, y_{A, \mathrm{start}})$, and $\mathbf{b} = (x_{B, \mathrm{start}}, y_{B, \mathrm{start}}, x_{B, \mathrm{end}}, y_{B, \mathrm{end}})$. 
	We then define our distance measure as $d(A, B) :=  \min \left\{ d_e(\mathbf{a}_1, \mathbf{b}), d_e(\mathbf{a}_2, \mathbf{b}) \right\}$, for the euclidean distance $d_e$ in $\mathbb{R}^4$. 
	This function measures the distance between the endpoints irrespective of their ordering, which means that a trajectory that starts from point A and ends at point B will be close to a trajectory that starts from point B and ends at point A.
	The scale of the datasets we tested on had large enough spatial scale that clustering based on endpoints captured people moving from destination to destination, e.g. from a storefront to the sidewalk at the edge of a scene. On this dataset, distance functions that utilize the entire trajectory such as DTW, LCSS, and PF from \cite{Morris2009} and TRACLUS from \cite{Lee2007} did not identify pedestrian intent as well as our method did. While it is unclear why TRACLUS underperformed on our data, PF, DTW, and LCSS appeared to put trajectories that were very similar for periods of time together even though they had very different intents.}

@@

\end{item}

\begin{item}
\textbf{Adequacy of Citation
I believe literature review section can be improved using a sub section
on social force models, which is extensively applied for pedestrian
trajectory forecasting. 
Helbing and Molnar, 1995; Koppula and Saxena, 2013; Pellegrini et al.,
2010; Yamaguchi et al., 2011; Xu et al., 2012; Wang et al. 2008;
Hospedales et al. 2009; Emonet et al. 2011; Yi et al. 2015.}
\end{item}

We agree that this adds to the paper, thank you for the suggestion. 
We added the following section to our literature review to reflect the relevant work:

\reversemarginpar\marginnote{\#1.1}
	\response{Many authors have approached pedestrian forecasting by deriving their motion model from interactions between pedestrians using physically motivated methods \cite{Helbing1995,Xu2012}. 
	Several models derive their motion models from \cite{Helbing1995} by incorporating collision avoidance through an interaction potential \cite{Pellegrini2009,Yamaguchi2011,Yi2016}. 
	However this method suffers from not planning for other pedestrian positions at future times. 
	Others take optical flow as input \cite{Hospedales2009,Wang2009,Emonet2011}.
	These approaches use variants of Hierarchical Dirichlet Processes on discretized optical flow to determine temporal motifs (i.e. classes of motion within the scene), or on a Markov model. 
	 These models are not agent based, and the lack of an explicit motion model limits their predictive power. 
	 Recently methods have been developed to predict trajectories by introducing and sampling Anticipatory Temporal Conditional Random Fields which incorporate learned affordances for humans and objects based on observed objectives within the scene \cite{Koppula2016}. 
	 Others create agent-based models based on Gaussian Processes, though they suffer issues when trained on discretized trajectories \cite{Tay2008,Wang2008,Trautman2015}. 
	Most recently a method using Long Short-Term Memory (lstm) to learn pedestrian motion models without making assumptions about the manner in which agents interact and is the state-of-the-art algorithm for socially based models while also having a rapid computation time \cite{Alahi2016}.}

@@

\end{item}

\end{enumerate}

\section*{Reviewer 5}
\begin{enumerate}
\begin{item}
\textbf{
It would be more interesting if the authors show whether
the prediction algorithm would transfer the learned ``knowledge" of
forecasting in novel scenes.}

Thank you for your comment. 
Though this was not the focus of this paper, the low-dimensional parameterization of the vector fields make transfer learning more amenable. 
As it is, this is an immediate avenue for future work which we describe in the following addition to the text: 
\reversemarginpar\marginnote{\#5.2}
\response{We also plan to explore transfer learning using scene segmentation, as well as the semantic context descriptors and routing scores to show how vector fields can be transferred to novel scenes. It appears that the low-order parameterization and unit-length vector field of our model, make it amenable to the methods developed in \cite{Ballan2016}.}

### 2017-06-09 revision/paper/response_for_essay.tex

\documentclass[usenames,dvipsnames]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[letterpaper, total={6in, 8in}]{geometry}
\usepackage{color}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{marginnote}
\usepackage{subcaption}

\newcommand{\todo}[1]{\textcolor{red}{#1}}
\newcommand{\Ram}[1]{{\normalsize{\textbf{({\color{green}Ram:\ }#1)}}}}
\providecommand{\response}[1]{
\noindent
\noindent\colorbox{gray!20}{
\parbox{\textwidth}{
\setlength{\parskip}{.1in}
\setlength{\parindent}{.1in}
#1}
}
}

\title{\LARGE A Representative Sample of My Writing \\ \textbf{Author's Response} }

@@

\author{Henry O. Jacobs, Owen K. Hughes, \\ Matt Johnson-Roberson, and Ram Vasudevan }

\begin{document}
\maketitle

%\todo{More formal version of: We would like to thank the reviewers for their comments. The feedback is very helpful, and we have attempted to address everything.}

I have not uploaded the incorrect document. Through this assignment you are seeking a representative sample of my writing. I have herein provided a sample of my writing. My intent is not to pursue a career in the humanities, rather it is to pursue a Ph.D. in the mathematical sciences. As a professor in a technical field you advance by writing papers for publication in peer-reviewed journals. After submission, manuscripts are returned with criticisms made by experts in your field. These criticisms must be addressed by the authors. I am co-author on a paper submitted to the IEEE Robotics and Automation Letters. After the initial submission of which I penned several sections, the first author left our research group to go into industry. I stepped up and did the revisions. The proceeding document is the letter I wrote as a supplement to our resubmitted manuscript which explains the changes I made to the paper itself. The figures have been ommitted. This is an example of my writing proficiency; though not the style you requested, it is the style that matters in my career path. If the reader cares to read the full manuscript, I would be more than willing to go over it in person and outline my contributions as well as the argumentative structure of the document, however I have not included it here because of its pending publication.

We would like to begin by thanking the reviewers and the editor for their careful reading and review of our paper.
The comments provided were incredibly helpful and insightful, and have strengthened the paper considerably.
Based on the recommendations of the reviewers and the editor, we have made several modifications to the paper including performing additional analyses with an lstm-based approach and using the Modified Hausdorff Distance metric. 
These additions pushed the paper beyond the eight page limit. 
As a result we removed all proofs from the resubmitted manuscript, but have included them instead in a supplementary technical report with our resubmission.
This technical report will be posted to our websites if the paper is accepted. 
%The changes made are presented below as a highlighted manuscript that indicates additions in green and removals in red.
The changes made are summarized in detail in the letter below. \textbf{This letter is largely self contained, so references here are to the bibliography in this document}.
% See the response to reviewers for a detailed breakdown of the changes made.

### 2017-06-09 final/technicalreport/pedestrian_forecasting_iros_2017-technicalreport.tex
Create final version of the paper.

% paper title
\title{Real-Time Certified Probabilistic Pedestrian Forecasting}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{./figures/MHD_results.eps}
	\caption{A comparison of the MHD from the ground truth of the pedestrian to a 1000 point samples from each distribution. The method from \cite{Alahi2016} does well at short time scales since it places a highly confident distribution at the given initial position of the pedestrian, but the method developed in this paper outperforms all others at intermediate times. \cite{Kitani2012}, which requires the end point of each trajectory, outperforms all other algorithms at longer time scales since they assume that the end point of the trajectory is unknown.}
%	\reversemarginpar\marginnote{\#4.8}
	\label{fig:mhd_vs_time}
	\vspace*{-0.7cm}
\end{figure}

>>>>

% paper title
\title{\textbf{Technical Report:} \\ Real-Time Certified Probabilistic Pedestrian Forecasting}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{./figures/MHD_results.eps}
	\caption{A comparison of the MHD from the ground truth of the pedestrian to a 1000 point samples from each distribution. The method from \cite{Alahi2016} does well at short time scales since it places a highly confident distribution at the given initial position of the pedestrian, but the method developed in this paper outperforms all others at intermediate times. \cite{Kitani2012}, which requires the end point of each trajectory, outperforms all other algorithms at longer time scales since they assume that the end point of the trajectory is known.}
%	\reversemarginpar\marginnote{\#4.8}
	\label{fig:mhd_vs_time}
	\vspace*{-0.7cm}
\end{figure}
